---
title: "2 Week R Code"
author: "C M Newman"
date: "6/8/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Same code, 2 weeks:
```{r}
setwd("/Users/charlottenewman/Downloads/BAM/Thesis/Data")
library(readxl)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(readr)
library(scales)
library(stargazer)
library(gridExtra)
library(psych) #describe() function
library(plm)
library(lubridate)
library(ggpubr)
library("tidymodels")
library("glmnet")
library("kernlab")
library("skimr")
library(fastDummies)
library(olsrr)
library(GGally)
library(glmnet)
library(jtools)
library(ggstance)
library(ggpubr)
library("lmtest")
library(vtable)
library(standardize)
library(car)
```

```{r}
pros_A_2w <- read.csv("Prospects A Charlotte.csv", sep = "\t")
pros_B_2w <- read.csv("Prospects B Charlotte.csv", sep = "\t")
pros_C_2w <- read.csv("Prospects C Charlotte.csv", sep = "\t")
ret_A_2w <- read_excel("Ret A Charlotte.xlsx")
ret_B_2w <- read.csv("Ret B Charlotte.csv", sep = "\t")
ret_C_2w <- read.csv("Ret C Charlotte.csv", sep = "\t")

names(pros_A_2w)[names(pros_A_2w) == "Customer.code..Recipient."] <- "Customer_Code"
names(pros_B_2w)[names(pros_B_2w) == "Customer.code..Recipient."] <- "Customer_Code"
names(pros_C_2w)[names(pros_C_2w) == "Customer.code..Recipient."] <- "Customer_Code"
names(ret_A_2w)[names(ret_A_2w) == "Customer code (Recipient)"] <- "Customer_Code"
names(ret_B_2w)[names(ret_B_2w) == "Customer.code..Recipient."] <- "Customer_Code"
names(ret_C_2w)[names(ret_C_2w) == "Customer.code..Recipient."] <- "Customer_Code"

pros_A_2w <- left_join(pros_A_2w, customer_data, by = "Customer_Code")
pros_B_2w <- left_join(pros_B_2w, customer_data, by = "Customer_Code")
pros_C_2w <- left_join(pros_C_2w, customer_data, by = "Customer_Code")
ret_A_2w <- left_join(ret_A_2w, customer_data, by = "Customer_Code")
ret_B_2w <- left_join(ret_B_2w, customer_data, by = "Customer_Code")
ret_C_2w <- left_join(ret_C_2w, customer_data, by = "Customer_Code")

pros_A_2w <- left_join(pros_A_2w, HA_Sales_Hist_Det, by = "Customer_Code")
pros_B_2w <- left_join(pros_B_2w, HA_Sales_Hist_Det, by = "Customer_Code")
pros_C_2w <- left_join(pros_C_2w, HA_Sales_Hist_Det, by = "Customer_Code")
ret_A_2w <- left_join(ret_A_2w, HA_Sales_Hist_Det, by = "Customer_Code")
ret_B_2w <- left_join(ret_B_2w, HA_Sales_Hist_Det, by = "Customer_Code")
ret_C_2w <- left_join(ret_C_2w, HA_Sales_Hist_Det, by = "Customer_Code")

pros_A_2w <- left_join(pros_A_2w, HT_Hearing_Loss, by = "Customer_Code")
pros_B_2w <- left_join(pros_B_2w, HT_Hearing_Loss, by = "Customer_Code")
pros_C_2w <- left_join(pros_C_2w, HT_Hearing_Loss, by = "Customer_Code")
ret_A_2w <- left_join(ret_A_2w, HT_Hearing_Loss, by = "Customer_Code")
ret_B_2w <- left_join(ret_B_2w, HT_Hearing_Loss, by = "Customer_Code")
ret_C_2w <- left_join(ret_C_2w, HT_Hearing_Loss, by = "Customer_Code")

pros_A_2w <- left_join(pros_A_2w, HT_Hist_Det, by = "Customer_Code")
pros_B_2w <- left_join(pros_B_2w, HT_Hist_Det, by = "Customer_Code")
pros_C_2w <- left_join(pros_C_2w, HT_Hist_Det, by = "Customer_Code")
ret_A_2w <- left_join(ret_A_2w, HT_Hist_Det, by = "Customer_Code")
ret_B_2w <- left_join(ret_B_2w, HT_Hist_Det, by = "Customer_Code")
ret_C_2w <- left_join(ret_C_2w, HT_Hist_Det, by = "Customer_Code")

pros_A_2w$Historic_HA_Purchases[is.na(pros_A_2w$Historic_HA_Purchases)] <- 0
pros_B_2w$Historic_HA_Purchases[is.na(pros_B_2w$Historic_HA_Purchases)] <- 0
pros_C_2w$Historic_HA_Purchases[is.na(pros_C_2w$Historic_HA_Purchases)] <- 0
pros_A_2w <- pros_A_2w[pros_A_2w$Historic_HA_Purchases == 0, ]
pros_B_2w <- pros_B_2w[pros_B_2w$Historic_HA_Purchases == 0, ]
pros_C_2w <- pros_C_2w[pros_C_2w$Historic_HA_Purchases == 0, ]

names(pros_A_2w)[names(pros_A_2w) == "Historic_campaings"] <- "Historic_Campaigns"
names(pros_B_2w)[names(pros_B_2w) == "Historic_campaings"] <- "Historic_Campaigns"
names(pros_C_2w)[names(pros_C_2w) == "Historic_campaings"] <- "Historic_Campaigns"
names(ret_A_2w)[names(ret_A_2w) == "Historic_campaings"] <- "Historic_Campaigns"
names(ret_B_2w)[names(ret_B_2w) == "Historic_campaings"] <- "Historic_Campaigns"
names(ret_C_2w)[names(ret_C_2w) == "Historic_campaings"] <- "Historic_Campaigns"

names(pros_A_2w)[names(pros_A_2w) == "Laatste_Hoortoestel_Koop"] <- "Last_HA_Purchase"
names(pros_B_2w)[names(pros_B_2w) == "Laatste_Hoortoestel_Koop"] <- "Last_HA_Purchase"
names(pros_C_2w)[names(pros_C_2w) == "Laatste_Hoortoestel_Koop"] <- "Last_HA_Purchase"
names(ret_A_2w)[names(ret_A_2w) == "Laatste_Hoortoestel_Koop"] <- "Last_HA_Purchase"
names(ret_B_2w)[names(ret_B_2w) == "Laatste_Hoortoestel_Koop"] <- "Last_HA_Purchase"
names(ret_C_2w)[names(ret_C_2w) == "Laatste_Hoortoestel_Koop"] <- "Last_HA_Purchase"
```

prepare dependent variable data:
```{r}
#If the last appointment/booking was after the newsletter was sent, we attribute the email as the cause of this. 
#If it was after the email = 1, if the last booking was before the email = 0.
#This is my DEPENDENT variable.
names(pros_A_2w)[names(pros_A_2w) == "Laatste_Hoortest"] <- "Booked_Appointment"
names(pros_B_2w)[names(pros_B_2w) == "Laatste_Hoortest"] <- "Booked_Appointment"
names(pros_C_2w)[names(pros_C_2w) == "Laatste_Hoortest"] <- "Booked_Appointment"
names(ret_A_2w)[names(ret_A_2w) == "Laatste_Hoortest"] <- "Booked_Appointment"
names(ret_B_2w)[names(ret_B_2w) == "Laatste_Hoortest"] <- "Booked_Appointment"
names(ret_C_2w)[names(ret_C_2w) == "Laatste_Hoortest"] <- "Booked_Appointment"


pros_A_2w$Booked_Appointment <- ifelse(pros_A_2w$Booked_Appointment > as.Date("2022/04/05", format = "%Y/%m/%d"), 1, 0)
pros_B_2w$Booked_Appointment <- ifelse(pros_B_2w$Booked_Appointment > as.Date("2022/04/05", format = "%Y/%m/%d"), 1, 0)
pros_C_2w$Booked_Appointment <- ifelse(pros_C_2w$Booked_Appointment > as.Date("2022/04/05", format = "%Y/%m/%d"), 1, 0)
ret_A_2w$Booked_Appointment <- ifelse(ret_A_2w$Booked_Appointment > as.Date("2022/04/05", format = "%Y/%m/%d"), 1, 0)
ret_B_2w$Booked_Appointment <- ifelse(ret_B_2w$Booked_Appointment > as.Date("2022/04/05", format = "%Y/%m/%d"), 1, 0)
ret_C_2w$Booked_Appointment <- ifelse(ret_C_2w$Booked_Appointment > as.Date("2022/04/05", format = "%Y/%m/%d"), 1, 0)
```

prepare independent variable data:
```{r}
#keep only the LATEST row of the customer, removing duplicates
pros_A_2w <- distinct(pros_A_2w, Customer_Code, .keep_all = TRUE)
pros_B_2w <- distinct(pros_B_2w, Customer_Code, .keep_all = TRUE)
pros_C_2w <- distinct(pros_C_2w, Customer_Code, .keep_all = TRUE)
ret_A_2w <- distinct(ret_A_2w, Customer_Code, .keep_all = TRUE)
ret_B_2w <- distinct(ret_B_2w, Customer_Code, .keep_all = TRUE)
ret_C_2w <- distinct(ret_C_2w, Customer_Code, .keep_all = TRUE)



#years since they've done their first hearing test until receiving the email
pros_A_2w$email_date <- ymd("2022/04/05")
pros_B_2w$email_date <- ymd("2022/04/05")
pros_C_2w$email_date <- ymd("2022/04/05")
ret_A_2w$email_date <- ymd("2022/04/05")
ret_B_2w$email_date <- ymd("2022/04/05")
ret_C_2w$email_date <- ymd("2022/04/05")

pros_A_2w$Customer_Tenure <- difftime(pros_A_2w$email_date, pros_A_2w$Eerste_Hoortest)
pros_A_2w$Customer_Tenure <- (pros_A_2w$Customer_Tenure)/365
pros_A_2w$Customer_Tenure <- as.integer(pros_A_2w$Customer_Tenure)

pros_B_2w$Customer_Tenure <- difftime(pros_B_2w$email_date, pros_B_2w$Eerste_Hoortest)
pros_B_2w$Customer_Tenure <- (pros_B_2w$Customer_Tenure)/365
pros_B_2w$Customer_Tenure <- as.integer(pros_B_2w$Customer_Tenure)

pros_C_2w$Customer_Tenure <- difftime(pros_C_2w$email_date, pros_C_2w$Eerste_Hoortest)
pros_C_2w$Customer_Tenure <- (pros_C_2w$Customer_Tenure)/365
pros_C_2w$Customer_Tenure <- as.integer(pros_C_2w$Customer_Tenure)

ret_A_2w$Customer_Tenure <- difftime(ret_A_2w$email_date, ret_A_2w$Eerste_Hoortest)
ret_A_2w$Customer_Tenure <- (ret_A_2w$Customer_Tenure)/365
ret_A_2w$Customer_Tenure <- as.integer(ret_A_2w$Customer_Tenure)

ret_B_2w$Customer_Tenure <- difftime(ret_B_2w$email_date, ret_B_2w$Eerste_Hoortest)
ret_B_2w$Customer_Tenure <- (ret_B_2w$Customer_Tenure)/365
ret_B_2w$Customer_Tenure <- as.integer(ret_B_2w$Customer_Tenure)

ret_C_2w$Customer_Tenure <- difftime(ret_C_2w$email_date, ret_C_2w$Eerste_Hoortest)
ret_C_2w$Customer_Tenure <- (ret_C_2w$Customer_Tenure)/365
ret_C_2w$Customer_Tenure <- as.integer(ret_C_2w$Customer_Tenure)

names(pros_A_2w)[names(pros_A_2w) == "Klant_Geslacht"] <- "Gender"
names(pros_B_2w)[names(pros_B_2w) == "Klant_Geslacht"] <- "Gender"
names(pros_C_2w)[names(pros_C_2w) == "Klant_Geslacht"] <- "Gender"
names(ret_A_2w)[names(ret_A_2w) == "Klant_Geslacht"] <- "Gender"
names(ret_B_2w)[names(ret_B_2w) == "Klant_Geslacht"] <- "Gender"
names(ret_C_2w)[names(ret_C_2w) == "Klant_Geslacht"] <- "Gender"

#gender binary: 0 = female, 1 = male
pros_A_2w$Gender <- ifelse(pros_A_2w$Gender == "M", 1, 0)
pros_B_2w$Gender <- ifelse(pros_B_2w$Gender == "M", 1, 0)
pros_C_2w$Gender <- ifelse(pros_C_2w$Gender == "M", 1, 0)
ret_A_2w$Gender <- ifelse(ret_A_2w$Gender == "M", 1, 0)
ret_B_2w$Gender <- ifelse(ret_B_2w$Gender == "M", 1, 0)
ret_C_2w$Gender <- ifelse(ret_C_2w$Gender == "M", 1, 0)



#add columns for prospect vs retention binary, and which treatment group binary
pros_A_2w$prevention <- 1
pros_B_2w$prevention <- 0
pros_C_2w$prevention <- 0
pros_A_2w$promotion <- 0
pros_B_2w$promotion <- 1
pros_C_2w$promotion <- 0
pros_A_2w$control <- 0
pros_B_2w$control <- 0
pros_C_2w$control <- 1
pros_A_2w$prospect <- 1
pros_B_2w$prospect <- 1
pros_C_2w$prospect <- 1
pros_A_2w$retention <- 0
pros_B_2w$retention <- 0
pros_C_2w$retention <- 0

ret_A_2w$prevention <- 1
ret_B_2w$prevention <- 0
ret_C_2w$prevention <- 0
ret_A_2w$promotion <- 0
ret_B_2w$promotion <- 1
ret_C_2w$promotion <- 0
ret_A_2w$control <- 0
ret_B_2w$control <- 0
ret_C_2w$control <- 1
ret_A_2w$prospect <- 0
ret_B_2w$prospect <- 0
ret_C_2w$prospect <- 0
ret_A_2w$retention <- 1
ret_B_2w$retention <- 1
ret_C_2w$retention <- 1

```

full dataset:
```{r}
full_data2w <- rbind(pros_A_2w, pros_B_2w, pros_C_2w, ret_A_2w, ret_B_2w, ret_C_2w)
full_data2w$Max_Hearing_Loss <- abs(full_data2w$Max_Hearing_Loss)

#change last few variables to english translation
names(full_data2w)[names(full_data2w) == "Klant_Geboortedatum"] <- "Birthday"
names(full_data2w)[names(full_data2w) == "Zorggroep_Naam"] <- "Insurance_Company"
names(full_data2w)[names(full_data2w) == "Eerste_Hoortoestel"] <- "First_HA"
names(full_data2w)[names(full_data2w) == "Eerste_Hoortest"] <- "First_HT"
names(full_data2w)[names(full_data2w) == "Klant_Plaats"] <- "Location"
names(full_data2w)[names(full_data2w) == "Leeftijd"] <- "Age"

full_data2w$Max_Hearing_Loss <- ifelse(full_data2w$Max_Hearing_Loss >= 35, 1, 0)
```

descriptive summary statistics:
```{r}
st(full_data2w, group = 'prospect', group.test = TRUE, out = 'latex')
#no significant diff in means
```

randomisation check:
prospects:
```{r}
prospects_rando_2w <- subset(full_data2w, prospect == 1, select = c(Date:retention))

prospects_prev_vs_contr_2w <- subset(prospects_rando_2w, promotion != 1, select = c(Date:retention))
prospects_promo_vs_contr_2w <- subset(prospects_rando_2w, prevention != 1, select = c(Date:retention))


st(prospects_prev_vs_contr_2w, group = 'prevention', group.test = TRUE, out = 'latex')
st(prospects_promo_vs_contr_2w, group = 'promotion', group.test = TRUE, out = 'latex')
#combine manually on latex
```

retention:
```{r}
retention_rando_2w <- subset(full_data2w, retention == 1, select = c(Date:retention))

retention_prev_vs_contr_2w <- subset(retention_rando_2w, promotion != 1, select = c(Date:retention))
retention_promo_vs_contr_2w <- subset(retention_rando_2w, prevention != 1, select = c(Date:retention))


st(retention_prev_vs_contr_2w, group = 'prevention', group.test = TRUE, out = 'latex')
st(retention_promo_vs_contr_2w, group = 'promotion', group.test = TRUE, out = 'latex')
#combine manually on latex
```

scaling the data (normalisation) + Control Regression:
```{r}
#to back track a scale() function: data$variable * attr(data$variable, 'scaled:scale') + attr(data$variable, 'scaled:center')
full_data_scaled_2w <- full_data2w

regression_vars_2w <- c("Age", "Gender", "Customer_Tenure", "Historic_Campaigns", "Historic_HA_Purchases", "Historic_purchases", "Max_Hearing_Loss", "Last_HearingTest", "retention", "promotion", "prevention")
scaled_vars_2w <- c("Age", "Gender", "Customer_Tenure", "Historic_Campaigns", "Historic_HA_Purchases", "Historic_purchases", "Max_Hearing_Loss", "Last_HearingTest")
regression_unscaled_vars_2w <- c("Booked_Appointment", "retention", "promotion", "prevention")

regression_unscaled_vars_2w <- full_data_scaled_2w[regression_unscaled_vars_2w]

xvars_scaled_2w <- full_data_scaled_2w[scaled_vars_2w]
xvars_scaled_2w <- scale(xvars_scaled_2w)
mean(xvars_scaled_2w, na.rm = TRUE)
sd(xvars_scaled_2w, na.rm = TRUE)

regression_vars_complete_2w <- cbind(xvars_scaled_2w, regression_unscaled_vars_2w)

regression_control_2w <- lm(Booked_Appointment ~ Age + Gender + Customer_Tenure + Historic_Campaigns + Historic_purchases + Max_Hearing_Loss + Last_HearingTest + retention + promotion + prevention, data = regression_vars_complete_2w)

bptest(regression_control_2w) # to test for heteroskedasticity.
#p < 0.5 (by a lot), so continue normally.

regression_control_2w <- coeftest(regression_control_2w, vcov = vcovHC(regression_control_2w, type="HC1"))

summary(regression_control_2w)

stargazer(regression_control_2w, type = "latex")
```

Prospects Regression:
```{r}
pros_regression_vars_2w <- c("Age", "Gender", "Customer_Tenure", "Historic_Campaigns", "Historic_HA_Purchases", "Historic_purchases", "Max_Hearing_Loss", "Last_HearingTest", "promotion", "prevention")
pros_scaled_vars_2w <- c("Age", "Gender", "Customer_Tenure", "Historic_Campaigns", "Historic_HA_Purchases", "Historic_purchases", "Max_Hearing_Loss", "Last_HearingTest")
pros_regression_unscaled_vars_2w <- c("Booked_Appointment", "retention", "promotion", "prevention")

pros_regression_unscaled_vars_2w <- full_data_scaled_2w[pros_regression_unscaled_vars_2w]

pros_xvars_scaled_2w <- full_data_scaled_2w[pros_scaled_vars_2w]
pros_xvars_scaled_2w <- scale(pros_xvars_scaled_2w )
mean(pros_xvars_scaled_2w, na.rm = TRUE)
sd(pros_xvars_scaled_2w, na.rm = TRUE)

pros_regression_vars_complete_2w <- cbind(pros_xvars_scaled_2w, pros_regression_unscaled_vars_2w)
pros_regression_vars_complete_2w <- subset(pros_regression_vars_complete_2w, retention == 0, select = c(Age:prevention))

regression_prospects_2w <- lm(Booked_Appointment ~ Age + Gender + Customer_Tenure + Historic_Campaigns + Historic_purchases + Max_Hearing_Loss + Last_HearingTest + promotion + prevention, data = pros_regression_vars_complete_2w)

bptest(regression_prospects_2w) # to test for heteroskedasticity.
#p < 0.5 (by a lot), so continue normally.

regression_prospects_2w <- coeftest(regression_prospects_2w, vcov = vcovHC(regression_prospects_2w, type="HC1"))

summary(regression_prospects_2w)

stargazer(regression_prospects_2w, type = "latex")

```

retention regression:
```{r}
ret_regression_vars_2w <- c("Age", "Gender", "Customer_Tenure", "Historic_Campaigns", "Historic_HA_Purchases", "Historic_purchases", "Max_Hearing_Loss", "Last_HearingTest", "promotion", "prevention")
ret_scaled_vars_2w <- c("Age", "Gender", "Customer_Tenure", "Historic_Campaigns", "Historic_HA_Purchases", "Historic_purchases", "Max_Hearing_Loss", "Last_HearingTest")
ret_regression_unscaled_vars_2w <- c("Booked_Appointment", "retention", "promotion", "prevention")

ret_regression_unscaled_vars_2w <- full_data_scaled_2w[ret_regression_unscaled_vars_2w]

ret_xvars_scaled_2w <- full_data_scaled_2w[ret_scaled_vars_2w]
ret_xvars_scaled_2w <- scale(ret_xvars_scaled_2w)
mean(ret_xvars_scaled_2w, na.rm = TRUE)
sd(ret_xvars_scaled_2w, na.rm = TRUE)

ret_regression_vars_complete_2w <- cbind(ret_xvars_scaled_2w, ret_regression_unscaled_vars_2w)
ret_regression_vars_complete_2w <- subset(ret_regression_vars_complete_2w, retention == 1, select = c(Age:prevention))

regression_retention_2w <- lm(Booked_Appointment ~ Age + Gender + Customer_Tenure + Historic_Campaigns + Historic_HA_Purchases + Historic_purchases + Max_Hearing_Loss + Last_HearingTest + promotion + prevention, data = ret_regression_vars_complete_2w)

bptest(regression_retention_2w) # to test for heteroskedasticity.
#p < 0.5 (by a lot), so continue normally.

regression_retention_2w <- coeftest(regression_retention_2w, vcov = vcovHC(regression_retention_2w, type="HC1"))

summary(regression_retention_2w)

stargazer(regression_prospects_2w, regression_retention_2w, type = "latex")

```



ALTERNATIVE DEPENDENT VAR 1 (Type)
scaling the data (normalisation) + Control Regression:
```{r}
#to back track a scale() function: data$variable * attr(data$variable, 'scaled:scale') + attr(data$variable, 'scaled:center')
full_data_type_2w <- full_data
ifelse(full_data_type_2w$Type == 2, 1, 0)
full_data_scaled_2w_alt1 <- full_data_type_2w

regression_vars_2w_alt1 <- c("Age", "Gender", "Customer_Tenure", "Historic_Campaigns", "Historic_HA_Purchases", "Historic_purchases", "Max_Hearing_Loss", "Last_HearingTest", "retention", "promotion", "prevention")
scaled_vars_2w_alt1 <- c("Age", "Gender", "Customer_Tenure", "Historic_Campaigns", "Historic_HA_Purchases", "Historic_purchases", "Max_Hearing_Loss", "Last_HearingTest")
regression_unscaled_vars_2w_alt1 <- c("Type", "retention", "promotion", "prevention")

regression_unscaled_vars_2w_alt1 <- full_data_scaled_2w_alt1[regression_unscaled_vars_2w_alt1]

xvars_scaled_2w_alt1 <- full_data_scaled_2w_alt1[scaled_vars_2w_alt1]
xvars_scaled_2w_alt1 <- scale(xvars_scaled_2w_alt1)
mean(xvars_scaled_2w_alt1, na.rm = TRUE)
sd(xvars_scaled_2w_alt1, na.rm = TRUE)

regression_vars_complete_2w_alt1 <- cbind(xvars_scaled_2w_alt1, regression_unscaled_vars_2w_alt1)

regression_control_2w_alt1 <- lm(Type ~ Age + Gender + Customer_Tenure + Historic_Campaigns + Historic_purchases + Max_Hearing_Loss + Last_HearingTest + retention + promotion + prevention, data = regression_vars_complete_2w_alt1)

bptest(regression_control_2w_alt1) # to test for heteroskedasticity.
#p < 0.5 (by a lot), so do extra step
regression_control_2w_alt1 <- coeftest(regression_control_2w_alt1, vcov = vcovHC(regression_control_2w_alt1, type="HC1"))

summary(regression_control_2w_alt1)

stargazer(regression_control_2w_alt1, type = "latex")
```

Prospects Regression:
```{r}
pros_regression_vars_2w_alt1 <- c("Age", "Gender", "Customer_Tenure", "Historic_Campaigns", "Historic_HA_Purchases", "Historic_purchases", "Max_Hearing_Loss", "Last_HearingTest", "promotion", "prevention")
pros_scaled_vars_2w_alt1 <- c("Age", "Gender", "Customer_Tenure", "Historic_Campaigns", "Historic_HA_Purchases", "Historic_purchases", "Max_Hearing_Loss", "Last_HearingTest")
pros_regression_unscaled_vars_2w_alt1 <- c("Type", "retention", "promotion", "prevention")

pros_regression_unscaled_vars_2w_alt1 <- full_data_scaled_2w_alt1[pros_regression_unscaled_vars_2w_alt1]

pros_xvars_scaled_2w_alt1 <- full_data_scaled_2w_alt1[pros_scaled_vars_2w_alt1]
pros_xvars_scaled_2w_alt1 <- scale(pros_xvars_scaled_2w_alt1)
mean(pros_xvars_scaled_2w_alt1, na.rm = TRUE)
sd(pros_xvars_scaled_2w_alt1, na.rm = TRUE)

pros_regression_vars_complete_2w_alt1 <- cbind(pros_xvars_scaled_2w_alt1, pros_regression_unscaled_vars_2w_alt1)
pros_regression_vars_complete_2w_alt1 <- subset(pros_regression_vars_complete_2w_alt1, retention == 0, select = c(Age:prevention))

regression_prospects_2w_alt1 <- lm(Type ~ Age + Gender + Customer_Tenure + Historic_Campaigns + Historic_purchases + Max_Hearing_Loss + Last_HearingTest + promotion + prevention, data = pros_regression_vars_complete_2w_alt1)

bptest(regression_prospects_2w_alt1) # to test for heteroskedasticity.
#p < 0.5 (by a lot), so do additional steps.

regression_prospects_2w_alt1 <- coeftest(regression_prospects_2w_alt1, vcov = vcovHC(regression_prospects_2w_alt1, type="HC1"))

summary(regression_prospects_2w_alt1)

stargazer(regression_prospects_2w_alt1, type = "latex")

```

retention regression:
```{r}
ret_regression_vars_2w_alt1 <- c("Age", "Gender", "Customer_Tenure", "Historic_Campaigns", "Historic_HA_Purchases", "Historic_purchases", "Max_Hearing_Loss", "Last_HearingTest", "promotion", "prevention")
ret_scaled_vars_2w_alt1 <- c("Age", "Gender", "Customer_Tenure", "Historic_Campaigns", "Historic_HA_Purchases", "Historic_purchases", "Max_Hearing_Loss", "Last_HearingTest")
ret_regression_unscaled_vars_2w_alt1 <- c("Type", "retention", "promotion", "prevention")

ret_regression_unscaled_vars_2w_alt1 <- full_data_scaled_2w_alt1[ret_regression_unscaled_vars_2w_alt1]

ret_xvars_scaled_2w_alt1 <- full_data_scaled_2w_alt1[ret_scaled_vars_2w_alt1]
ret_xvars_scaled_2w_alt1 <- scale(ret_xvars_scaled_2w_alt1)
mean(ret_xvars_scaled_2w_alt1, na.rm = TRUE)
sd(ret_xvars_scaled_2w_alt1, na.rm = TRUE)

ret_regression_vars_complete_2w_alt1 <- cbind(ret_xvars_scaled_2w_alt1, ret_regression_unscaled_vars_2w_alt1)
ret_regression_vars_complete_2w_alt1 <- subset(ret_regression_vars_complete_2w_alt1, retention == 1, select = c(Age:prevention))

regression_retention_2w_alt1 <- lm(Type ~ Age + Gender + Customer_Tenure + Historic_Campaigns + Historic_HA_Purchases + Historic_purchases + Max_Hearing_Loss + Last_HearingTest + promotion + prevention, data = ret_regression_vars_complete_2w_alt1)

bptest(regression_retention_2w_alt1) # to test for heteroskedasticity.
#p < 0.5 (by a lot), so continue normally.

regression_retention_2w_alt1 <- coeftest(regression_retention_2w_alt1, vcov = vcovHC(regression_retention_2w_alt1, type="HC1"))

summary(regression_retention_2w_alt1)

stargazer(regression_control_2w_alt1, regression_prospects_2w_alt1, regression_retention_2w_alt1, type = "latex")

```



ALTERNATIVE DEPENDENT VAR 2
scaling the data (normalisation) + Control Regression:
```{r}
#to back track a scale() function: data$variable * attr(data$variable, 'scaled:scale') + attr(data$variable, 'scaled:center')
full_data_unsub_2w <- full_data
ifelse(full_data_unsub_2w$Type == 3, 1, 0)
full_data_scaled_2w_alt2 <- full_data_unsub_2w

regression_vars_2w_alt2 <- c("Age", "Gender", "Customer_Tenure", "Historic_Campaigns", "Historic_HA_Purchases", "Historic_purchases", "Max_Hearing_Loss", "Last_HearingTest", "retention", "promotion", "prevention")
scaled_vars_2w_alt2 <- c("Age", "Gender", "Customer_Tenure", "Historic_Campaigns", "Historic_HA_Purchases", "Historic_purchases", "Max_Hearing_Loss", "Last_HearingTest")
regression_unscaled_vars_2w_alt2 <- c("Type", "retention", "promotion", "prevention")

regression_unscaled_vars_2w_alt2 <- full_data_scaled_2w_alt2[regression_unscaled_vars_2w_alt2]

xvars_scaled_2w_alt2 <- full_data_scaled_2w_alt2[scaled_vars_2w_alt2]
xvars_scaled_2w_alt2 <- scale(xvars_scaled_2w_alt2)
mean(xvars_scaled_2w_alt2, na.rm = TRUE)
sd(xvars_scaled_2w_alt2, na.rm = TRUE)

regression_vars_complete_2w_alt2 <- cbind(xvars_scaled_2w_alt2, regression_unscaled_vars_2w_alt2)

regression_control_2w_alt2 <- lm(Type ~ Age + Gender + Customer_Tenure + Historic_Campaigns + Historic_purchases + Max_Hearing_Loss + Last_HearingTest + retention + promotion + prevention, data = regression_vars_complete_2w_alt2)

bptest(regression_control_2w_alt2) # to test for heteroskedasticity.
#p < 0.5 (by a lot), so do extra step
regression_control_2w_alt2 <- coeftest(regression_control_2w_alt2, vcov = vcovHC(regression_control_2w_alt2, type="HC1"))

summary(regression_control_2w_alt2)

stargazer(regression_control_2w_alt2, type = "latex")
```

Prospects Regression:
```{r}
pros_regression_vars_2w_alt2 <- c("Age", "Gender", "Customer_Tenure", "Historic_Campaigns", "Historic_HA_Purchases", "Historic_purchases", "Max_Hearing_Loss", "Last_HearingTest", "promotion", "prevention")
pros_scaled_vars_2w_alt2 <- c("Age", "Gender", "Customer_Tenure", "Historic_Campaigns", "Historic_HA_Purchases", "Historic_purchases", "Max_Hearing_Loss", "Last_HearingTest")
pros_regression_unscaled_vars_2w_alt2 <- c("Type", "retention", "promotion", "prevention")

pros_regression_unscaled_vars_2w_alt2 <- full_data_scaled_2w_alt2[pros_regression_unscaled_vars_2w_alt2]

pros_xvars_scaled_2w_alt2 <- full_data_scaled_2w_alt2[pros_scaled_vars_2w_alt2]
pros_xvars_scaled_2w_alt2 <- scale(pros_xvars_scaled_2w_alt2)
mean(pros_xvars_scaled_2w_alt2, na.rm = TRUE)
sd(pros_xvars_scaled_2w_alt2, na.rm = TRUE)

pros_regression_vars_complete_2w_alt2 <- cbind(pros_xvars_scaled_2w_alt2, pros_regression_unscaled_vars_2w_alt2)
pros_regression_vars_complete_2w_alt2 <- subset(pros_regression_vars_complete_2w_alt2, retention == 0, select = c(Age:prevention))

regression_prospects_2w_alt2 <- lm(Type ~ Age + Gender + Customer_Tenure + Historic_Campaigns + Historic_purchases + Max_Hearing_Loss + Last_HearingTest + promotion + prevention, data = pros_regression_vars_complete_2w_alt2)

bptest(regression_prospects_2w_alt2) # to test for heteroskedasticity.
#p < 0.5 (by a lot), so do additional steps.

regression_prospects_2w_alt2 <- coeftest(regression_prospects_2w_alt2, vcov = vcovHC(regression_prospects_2w_alt2, type="HC1"))

summary(regression_prospects_2w_alt2)

stargazer(regression_prospects_alt2, type = "latex")

```

retention regression:
```{r}
ret_regression_vars_2w_alt2 <- c("Age", "Gender", "Customer_Tenure", "Historic_Campaigns", "Historic_HA_Purchases", "Historic_purchases", "Max_Hearing_Loss", "Last_HearingTest", "promotion", "prevention")
ret_scaled_vars_2w_alt2 <- c("Age", "Gender", "Customer_Tenure", "Historic_Campaigns", "Historic_HA_Purchases", "Historic_purchases", "Max_Hearing_Loss", "Last_HearingTest")
ret_regression_unscaled_vars_2w_alt2 <- c("Type", "retention", "promotion", "prevention")

ret_regression_unscaled_vars_2w_alt2 <- full_data_scaled_2w_alt2[ret_regression_unscaled_vars_2w_alt2]

ret_xvars_scaled_2w_alt2 <- full_data_scaled_2w_alt2[ret_scaled_vars_2w_alt2]
ret_xvars_scaled_2w_alt2 <- scale(ret_xvars_scaled_2w_alt2)
mean(ret_xvars_scaled_2w_alt2, na.rm = TRUE)
sd(ret_xvars_scaled_2w_alt2, na.rm = TRUE)

ret_regression_vars_complete_2w_alt2 <- cbind(ret_xvars_scaled_2w_alt2, ret_regression_unscaled_vars_2w_alt2)
ret_regression_vars_complete_2w_alt2 <- subset(ret_regression_vars_complete_2w_alt2, retention == 1, select = c(Age:prevention))

regression_retention_2w_alt2 <- lm(Type ~ Age + Gender + Customer_Tenure + Historic_Campaigns + Historic_HA_Purchases + Historic_purchases + Max_Hearing_Loss + Last_HearingTest + promotion + prevention, data = ret_regression_vars_complete_2w_alt2)

bptest(regression_retention_2w_alt2) # to test for heteroskedasticity.
#p < 0.5 (by a lot), so continue normally.

regression_retention_2w_alt2 <- coeftest(regression_retention_2w_alt2, vcov = vcovHC(regression_retention_2w_alt2, type="HC1"))

summary(regression_retention_2w_alt2)

stargazer(regression_control_2w_alt2, regression_prospects_2w_alt2, regression_retention_2w_alt2, type = "latex")

```





